---
title: "Alcohol vs Seat choice"
author: "Mya Orozco"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data


## Now add in boxplot
```{r}
boxplot(alcohol~Seat,data=davisdata)
```
 
 The boxes are not disjoint, if we look at the median of the back box it's higher than the other two box's. The front and middle boxes look almost the same.
  
### get fancy  



## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The front and back seats has around the same number of people but for the middle it has more than twice their numbers. While the middle seat had 32 people and the back seat had a max of 55 drinks which is significantly higher than the front and back seats.


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The probability of getting these kind of results are out of ten thousand. 

```{r}
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

The front and the back are different, the middle and the front are not different, now the back is different from the middle and the front. 

## Conclusions


Today started with making a box plot, the results on how much a row drinks of alcohol. Plus I also learned a new thing today, if there is three or more things to compare we can run a qualifying test that is "one way anova".
The probability was between 0 and 1 so I then investigated further and plotted another model that showed how different the back seats were.

