---
title: "Alcohol vs Seat choice"
author: "Mya Orozco"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data


## Now add in boxplot
```{r}
boxplot(alcohol~Seat,data=davisdata)
```
 
 The boxes are not disjoint, if we look at the median of the back box it's higher than the other two box's. The front and middle boxes look almost the same.
  
### get fancy  



## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The front and back seats has around the same number of people but for the back row it has more than twice their numbers. While the back seat had 32 people in the back seat had a max of 55 drinks which is significantly higher than the front and middle seats.


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The probability of getting these kind of results are out of ten thousand. 
## Conclusions


